A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
BIGGER
Add paragraph to Results section.

%Incorporating popularity has a large impact on the performance of any
%recommender and part of this is due simply to the evaluation metric. Any time we
%connect to a popular product, we are now two away from many more products,
%increasing the likelihood of getting a correct recommendation by the 2-precision
%standard. To ensure that these kinds of effects are not the sole reason that our
%recommender performs well, we construct the Popularity Recommender. This
%recommender simply recommends that every product in one catalogue be connected
%to the two most popular products from the other catalogue. This baseline shows
%how much of the LSI recommender's performance is due simply to leveraging
%popularity and how much is due to other factors, such as intelligently learning
%and mapping latent concepts.

@@

\begin{table}
\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
\end{tabular}
\caption{The performance of each of the recommenders across all categories. The
first five are the baseline recommenders outlined in the previous section. The
final three are the recommenders of interest, described in the Recommender
Algorithms section. The scores in bold are the most important results and are 
further illustrated in the following figure.}
\end{center}
\end{table}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.65\textwidth]{RecommenderPerformance2.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}
\pagebreak
\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.

>>>>

@@

\begin{table}
\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
\end{tabular}
\caption{The performance of each of the recommenders across all categories. The
first five are the baseline recommenders outlined in the previous section. The
final three are the recommenders of interest, described in the Recommender
Algorithms section. The scores in bold are the most important results and are 
further illustrated in the following figure.}
\end{center}
\end{table}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.65\textwidth]{RecommenderPerformance2.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}

Table (1) shows the results of all inter-catalogue recommenders across all
categories. For example, the {\em precision} column lists the sum, across all
categories, of correctly predicted edges divided by the sum, across all
categories, of predicted edges. We first point out that both $Neighborhood$ and
$LatentFeature$ outperform $ContentBased$ by all metrics. This makes clear the
utility of leveraging information from the recommendation when making
inter-catalogue recommendations. Next, we notice that $Neighborhood$ actually
outperforms $LatentFeature$ in {\em precision} by 10\% and in {\em 2-recall} by
about 5\%. Importantly, however, $LatentFeature$ bests $Neighborhood$ in the key
metric {\em 2-}$F_1$ by about 12\%.

\pagebreak
\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.
